
---
title: 'ELETRONIC SUPPLEMENTARY MATERIAL Background Noise as a Selective Pressure: Stream-breeding Anurans  Call at Higher Frequencies'
author: David Lucas Röhr; Gustavo B. Paterno; Felipe Camurugi; Flora A. Juncá; Adrian
  A. Garda;
date: "December 17, 2014"
output: pdf_document
toc: true
theme: "united"
---

***
>This doccument follows the principles of reproducible science (Peng, 2011). All Data and code required to repeat the analysis bellow are linked at [Github](https://github.com/paternogbc/2014_Rohr_et_al_JEB). To dowanload the __source code__ used to generate all figures, tables and analysis in the paper, please see: [source code](https://github.com/paternogbc/2014_Rohr_et_al_JEB/blob/master/R/Rhor_JEB_2014_source_code.R). This documment was generated in __R studio__ with `kintr` package.

\newpage



1. Packages versions:
===============================
```{r info,message=FALSE,echo=F}
info <- sessionInfo()
```

We used `r info[1]$R$ver` and the following packages:

```{r packages,message=FALSE,echo=T}
library(ape);library(caper);library(knitr)
library(dplyr);library(ggplot2);library(picante);library(gridExtra)
```

Please check the [Packages versions](https://github.com/paternogbc/2014_Rohr_et_al_JEB/blob/master/packrat/packrat.lock), for details.

```{r species data.entry,echo=F,results='hide'}
# Entrada de dados:
anura.data <- read.table("data/raw_data.csv",sep=",",h=T)
str(anura.data)
```
```{r phylogeny data entry,echo=F,results='hide'}
tree<-read.tree("phylogeny/amph_2014.tre")
tree.crop<-drop.tip(tree,as.character(anura.data[,1]))             
study.tree<-(drop.tip(tree,tree.crop$tip.label))
study.tree$node.label <- makeLabel(study.tree)$node.label 
comp.data <- comparative.data(phy=study.tree,data=anura.data,names.col="sp",vcv=T,vcv.dim=3)
```

\newpage

2. Data structure:
=================

2.1 Species data 
----------------
* To download __raw data__: [link](https://gist.github.com/paternogbc/d73612e22c36e538ee54).  
* To download __pdf table__ with data and references used: [link](https://github.com/paternogbc/2014_Rohr_et_al_JEB/blob/master/supp_material_Rohr_JEB_2014.pdf)

The species dataset contains six variables (see Methods for detailed information on data collection).  
  
variable  | discription
--------- | -----------
sp        | species name
environment| Reproductive environment (lentic or lotic)
DF| Dominant frequency (hertz)
SVL|snout-vent length (mm)
logDF| log10 of dominant frequency (DF)
logSVL| log10 of snout vent length (SVL)

Last six rows of the species dataset:

```{r,echo=F}
kable(tail(anura.data))
```

2.2 Phylogentic tree
--------------------
The phylogenetic tree used in this paper was pruned from: [Pyron and Wiens (2014)](http://www.sciencedirect.com/science/article/pii/S105579031100279X) anura super tree.  
* To dowanload the pruned tree with study species (509): [Study Tree]().  

```{r,echo=F,fig.height=6}
study.tree
comp.data$data$sp <- comp.data$tip.label
plot(comp.data[[1]],"fan",show.tip.label=T,cex=0.08,label.offset=1.2,
     lab4ut="axial")
tiplabels(frame="circle",col=comp.data$data$environment,
          pch=c(16,16),cex=0.3)
legend(legend=c("running","still"),pch=c(16,16),col=c("red","black"),
       "topleft",bty="n")
```

_Figure S1: Phylogeny for 509 anuran species sampled in this study extracted from Pyron and Wiens (2011) original tree. Black circles represent pond-breeding species (N = 332) and red circles stream-breeding species (N= 177)_

\newpage

2.3 Summary metrics for Dominant frequency and Sout-vent length
--------------------------------------------------------------------------
```{r data summery0,echo=F}
anura.data.summ <- summarise(group_by(anura.data,environment),meanDF=mean(DF),seDF=sd(DF),
                meanSVL=mean(SVL),seSVL=sd(SVL))
kable(anura.data.summ)
```

```{r datasummary1, message=FALSE,warning=FALSE,echo=FALSE,fig.height=3.5,fig.width=5.5,error=FALSE}
## DF:
g1 <- ggplot(anura.data,aes(x=logDF,fill=environment))+
geom_histogram(alpha=.5,position="identity")+
geom_vline(data=data.frame(anura.data.summ),aes(xintercept=log10(meanDF),colour=environment),linetype="dashed", size=1)+
xlab("Dominant Frequency (hertz)[log10]")+
theme(legend.position = c(0.2,.8),
      legend.background=element_rect("transparent"))

## SVL:
g2 <- ggplot(anura.data,aes(x=logSVL,fill=environment))+
geom_histogram(alpha=.5,position="identity")+
geom_vline(data=data.frame(anura.data.summ),aes(xintercept=log10(meanSVL),colour=environment),linetype="dashed", size=1)+
xlab("Sount-vent Length (mm)[log10]")+
theme(legend.position = "none")
grid.arrange(g1,g2,ncol=2)
```

_Figure S2: Distribution histograms for Dominant Frequency *(log10)* and Snout-vent length *(log10)*_

\newpage

3. Phylogenetic signal 
======================
3.1 Domiant Frequency and Snout-vent length
-------------------------------------------
We used K statistics to test the phylogentic signal for Dominant Frequency (*logDF*) and Snout-vent length(*logSVL*)(for details about the method, see [Blomberg et al (2003)](http://onlinelibrary.wiley.com/doi/10.1111/j.0014-3820.2003.tb00285.x/abstract)). 

```{r}
k.signal <- multiPhylosignal(select(comp.data$data,logDF,logSVL),comp.data$phy,reps=999)
kable(k.signal)
```
  
Dominant Frequency and Snout-Vent Length show significant phylogenetic signal, however, K values are low.  

3.2 Checking the phylogenetic signal of the residuals from stantard OLS regression
----------------------------------------------------------------------------------

In order to check the need to include the phylogeny in our analysis, first it is important to check if there is phylogenetic signal in the residuals of an Ordinary Least Square regression (OSL) (Kamilar & Cooper, 2013; Freckleton, 2009).

```{r,echo=T,message=FALSE,warning=FALSE}
mod.osl <- lm(logDF ~ environment*logSVL,anura.data)
# Extracting residuals from the model:
comp.data$data$lm.res <- residuals(mod.osl)
osl.resi.sig <- phylosignal(comp.data$data$lm.res,reps=999,comp.data$phy)
kable(osl.resi.sig)
```

Because the residuals from OSL regression show phylogenetic signal k = `r round(as.numeric(osl.resi.sig[1]),digits=2)`, it is necessary to correct for phylogenetic non-independence in data.  

\newpage

4. Data analysis 
========================================
We used a phylogenetic generalized least square model (PGLS) with dominant frequency as the response variable and reproduction habitat (lentic/lotic) and SVL as the explanatory variables to test if dominant frequency was affected by reproduction environment. Dominant frequencies and body sizes were log transformed (log10) before the analysis. To optimize branch length transformation, the lambda value was set by maximum likelihood (see [Freckleton et al., 2002](http://www.jstor.org/stable/10.1086/343873); [Orme et al., 2013](http://cran.r-project.org/web/packages/caper/vignettes/caper.pdf) for details). PGLS analysis were performed with the function `pgls` from the package `caper`.

4.1 Data preparation:
--------------------
Using the function `comparative.data` we combined our phylogenie with the species dataset
```{r,echo=FALSE}
comp.data <- comparative.data(phy=study.tree,data=anura.data,names.col="sp",vcv=T,vcv.dim=3)
comp.data 
```

4.2 Phylogenetic generalized least square model (PGLS)
--------------------
Fitting pgls model with with lambda adjusted by maximum likelihood:
```{r, cache=TRUE}
mod.pgls <- pgls(logDF ~ environment*logSVL, data=comp.data,lambda="ML")
summary(mod.pgls)
```

4.3 ANOVA table
---------------
```{r,echo=FALSE,cache=TRUE}
kable(anova(mod.pgls))
```

4.4 Confidence interval for lambda estimation
--------------------------------------------
```{r,fig.height=4,fig.width=4,cache=TRUE}
profile.lambda <- pgls.profile(mod.pgls)
plot(profile.lambda)
```

4.5 Model diagnostic:
--------------------

### 4.5.1 Standard graphic methods for model diagnostics   

```{r,echo=F,fig.height=5,fig.width=5}
par(mfrow=c(2,2))
plot(mod.pgls)
```

Residulas do not show any tendency. 

### 4.5.2 Phylogenetic signal of model residuals  
After performing PGLS analysis it is important to check the phylogenetic signal of model residuals.

```{r,warning=FALSE,message=FALSE}
k.residuals <- phylosignal(mod.pgls$phyres,reps=999,comp.data$phy)
kable(k.residuals)
```
  
Results above shows that the residuals do not present significant phylogenetic signal.

4.6 Model comparison: OSL vs PGLS
--------------------
```{r}
kable(AIC(mod.osl,mod.pgls))
```

AIC comparison shows that PGLS model has much lower AIC value round(`r AIC(mod.osl,mod.pgls)[2,2]`) then OSL model round(`r AIC(mod.osl,mod.pgls)[1,2]`). Thus, PGLS model is a better fit for the data.  

\newpage

5. References
=============
1. Pyron, R.A. & Wiens, J.J. 2011 A large-scale phylogeny of Amphibia including over 2800 species, and a revised classification of extant frogs, salamanders, and caecilians. Molecular Phylogenetics and Evolution 61, 543-583.  
2. Blomberg, S. P., T. Garland, Jr., and A. R. Ives. 2003. Testing for phylogenetic signal in comparative data: behavioral traits are more labile. Evolution 57:717-745.  
3. David Orme, Rob Freckleton, Gavin Thomas, Thomas Petzoldt, Susanne Fritz,
  Nick Isaac and Will Pearse (2013). caper: Comparative Analyses of
  Phylogenetics and Evolution in R. R package version 0.5.2.
  http://CRAN.R-project.org/package=caper   
4. Kamilar JM, Cooper N. 2013 Phylogenetic signal in primate behaviour, ecology and life history. Phil Trans R Soc B 368: 20120341. http://dx.doi.org/10.1098/rstb.2012.0341
5. Freckleton, R.P. (2009) The seven deadly sins of comparative analysis. J Evol Biol, 22, 1367-1375.  

***
When using the __data available__ in this paper, please cite the original publication.  
Contact davidlucasr@yahoo.com.br for any further information. 





